---
title: "combining_data"
author: "Adam A. Bramlett and Seth Wiener""
date: "2023-11-18"
output: html_document
---

```{r libraries, message=FALSE, error=FALSE}
library(tidyverse)
library(tidyr)
library(dplyr)
library(stringr)
library(readxl)
```
Here is some code for combining data frame


The code below is split into 5 chunks
-some file management set -up

3 methods for combining data by data type.
-the actual code we used in the Art of wrangling for combining data using plyr
-a simple for-loop solution
-an alternative tidyverse solution using a for loop and dplyr


At the end we have a small data column conversion code made to create easier variable names for the Art of Wrangling. This was necessary for making the paper readable. 


plyr solution: be careful if you are a tidyverse user. Plyr has overlapping arguments with dplyr. Be sure to detach it. However, this method is easy and straight forward with very little problems even with data that can have overlapping names. This is directly usable for the Gorilla data structure with relational data frame. Additional you can use argmuments for a pattern which is helpful if you have many tasks avaiable.
```{r}
#load all data
library(plyr)
#data eye_tracking

data_eyetracking<-plyr::ldply(list.files("/Users/xxusernamexx/scripts/et/eye_tracking/uploads", pattern="eyetracking", full.names=TRUE),function(filename) {
  dum=read_xlsx(filename)
  return(dum)
})

#load responses
data<-plyr::ldply(list.files("/Users/xxusernamexx/scripts/et/eye_tracking/", pattern="task", full.names=TRUE),function(filename) {
  dum=read.csv(filename)
  return(dum)
})

detach("package:plyr")
#this is only necessary if you have more than one eye-tracking task
task_dat <- data%>%filter(Task.Name == "Eye-tracking-task")
#our task had an additional bird song learning task with eye-tracking data for that as well
#bird_dat <- data%>%filter(Task.Name == "bird_tracking")
#load OSF data
OSF_df <- read.csv("xxx")
```
simple for loop: this is useful for situations that you just want to pull in all the data in a file and you know each spreadsheet is identical in form.
```{r}
dum<-read.csv(list[1],sep = "")
cols<-ncol(dum)+1
cols

data <- data.frame(matrix(ncol = cols, nrow = 0))
for (files in 1:length(list)){
  dum<-read.csv(list[files],sep = "")
  dum$name<-list[files]
  data<-rbind(data,dum)
} 
write.csv(data,"/Users/xxusernamexx/scripts/all_Mandarin_speakers/all_data.csv", row.names = FALSE)
```
for_loop+ dplyr solution--- this is useful when you have many spreadsheets that may have some form of inconsistency that you need to fix. Here, I was fixing the data types after loading in and providing the name of the file as a column name
```{r}
file_names<-list.files("/Users/xxusernamexx/scripts/kbi_data/",pattern = "data")
file_names
the_data<-data.frame(matrix(ncol = 1, nrow = 0))

for (file in file_names) {
  result <- list.files(paste("/Users/xxusernamexx/scripts/kbi_data/",file,"/",sep = ""),
                           pattern="one_[0-9]{4}-[0-9]{2}-[0-9]{2}_([A-Za-z0-9]+(.[A-Za-z0-9]+)+).csv",
                           full.names=TRUE)%>%
  map_df(~read_csv(.x)%>%mutate(across(.fns = as.character)))%>%
  type_convert()
  result$expName<-file
  result$participant<-as.numeric(result$participant)
  the_data<-bind_rows(the_data,result)
}

write.csv(all_data,file= "combined_data.csv")

```

#some name changes
```{r}
task_data<-task_dat
task_data[task_data == "Screen 1"] <- "gender"
task_data[task_data == "Screen 2"] <- "age"
task_data[task_data == "Screen 4"] <- "language_disorder"
task_data[task_data == "Screen 6"] <- "accent_heard"
task_data[task_data == "Screen 7"] <- "chinese_study_duration"
task_data[task_data == "Screen 8"] <- "experience_chinese_accent"
task_data[task_data == "Screen 9"] <- "other_languages_spoken"
task_data<-task_data%>%select(-c(Participant.Public.ID,Participant.External.Session.ID))

path<-"/Users/adambramlett/scripts/the_art_of_wrangling/data"
write.csv(task_data,file.path(path,"/task_data.csv"))
write.csv(data_eyetracking,file.path(path,"/et_data.csv"))
write.csv(OSF_df,file.path(path,"/OSF_data.csv"))
```