---
title: "meta_scrript_on_scripts"
author: "xxx"
date: "2023-11-21"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
# Function to extract line information from an Rmd file
extract_line_info_from_rmd <- function(file_path) {
  # Read the content of the Rmd file
  script <- readLines(file_path, warn = FALSE)
  
  # Create a data frame with line numbers and original content
  result <- data.frame(Line = seq_along(script), Content = script, stringsAsFactors = FALSE)
  
  
  return(result)
}


# Example usage
rmd_file_path <- "r_work_flow.Rmd"
line_nums<-extract_line_info_from_rmd(rmd_file_path)
line_nums$content_cleaned <- gsub("```", "", line_nums$Content)
line_nums$content_cleaned <- gsub("\\{r ", "", line_nums$content_cleaned)
line_nums$content_cleaned <- gsub("\\}", "", line_nums$content_cleaned)
line_nums$chunk <- gsub("[^`]+", "", line_nums$Content)
line_nums$chunk <- gsub("[^`]+", "", line_nums$Content)
#line_nums$content_cleaned <- gsub(" ", "", line_nums$content_cleaned)

line_nums2<-line_nums%>%
  filter(chunk=="```")%>%
  filter(Content!="```")%>%
  mutate(file_name = paste("\\",content_cleaned,".R",sep=""))%>%
  select(content_cleaned,Line)%>%
  filter(content_cleaned != "")

write.csv(line_nums2,"chunk-num_lister.csv")

```

```{r}

line_nums3<-line_nums%>%
  filter(chunk=="```")%>%
  filter(Content!="```")%>%
  mutate(file_name = paste("\\",content_cleaned,".R",sep=""))%>%
  select(content_cleaned,Line)%>%
  filter(content_cleaned != "")%>%
  mutate(var = paste("\\newcommand{\\var",content_cleaned,"}{",Line,"}",sep=""))%>%
  select(var)

writeLines(line_nums3$var, "var.tex")
```

